Bow shocks, bow waves, and dust waves

### 2018-05-23 papers/Papers1234/sec-dust-bow-intro.tex
Add new figure on drag force

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figs/drift-gn}
  \caption{Drift velocity versus FUV radiation parameter. Each line
    represents a model with ambient density and stellar type as
    indicated in the key.}
  \label{fig:drift-gn}
\end{figure*}

@@

>>>>

\begin{figure*}
  \includegraphics[width=\linewidth]{figs/gas-grain-drag-photoionized}
  \caption{Drag force as a function of gas--grain slip velocity,
    \(w\), for different values of the grain potential,
    \(\phi = U / k T\).  Contributions from proton and electron Coulomb
    (electrostatic) drag, as well as Epstein (solid-body) drag are
    indicated.  Inset shows \(\phi\) as a function of the radiation
    parameter, \(\Xi = P_{\mathrm{rad}} / P_{\mathrm{gas}}\) on a
    log--linear scale.}
  \label{fig:gas-grain-drag-photoionized}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figs/drift-pratio-4panel}
  \caption{Drift velocity versus radiation parameter \(\Xi_P\). Each line
    represents a model with ambient density and stellar type as
    indicated in the key.}
  \label{fig:drift-gn}
\end{figure*}

@@

If the radiation field is sufficiently strong, then the collisional coupling between grains and gas will break down.
